---
title: "Examples"
output:
  pdf_document:
    includes:
      in_header: macros.tex
  html_document: 
    includes:
      before_body: macros.html
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, comment = NA)
```

# Macros

### Set of real number

LaTeX: `\newcommand \RR {\mathbb{R}}` 

MathJax: `RR: "{\\mathbb{R}}"`

Call: `$\RR$`

Rendering: $\RR$ 

### Normal distribution

LaTeX: `\newcommand \normal [2] {\mathcal{N}\left({#1},{#2}\right)}` 

MathJax: `normal: ["{\\mathcal{N}\\left({#1},{#2}\\right)}", 2]`

Call: `$\normal{0}{\sigma^2}$`

Rendering: $\normal{0}{\sigma^2}$ 

### Differential operator

LaTeX: `\newcommand \dx [2] [] {\mathrm{d}^{#1}\mspace{-1mu}\mathord{#2}}` 

MathJax: `dx: ["{\\mathrm{d}^{#1}\\mspace{-1mu}\\mathord{#2}}", 2, ""]` 

Call: `$\dx{x} + \dx[2]{f}$`

Rendering: $\dx{x} + \dx[2]{f}$

### Colors in maths mode

LaTeX: `\usepackage{color}` + `\newcommand \warning [1] {\textcolor{red}{#1}}` 

MathJax: `warning: ["\\color{red}{{#1}}", 1]` 

Call: `$(a+b)^2 = a^2 + \warning{2ab} + b^2$`

Rendering: $(a+b)^2 = a^2 + \warning{2ab} + b^2$ 

### Colors in text mode 

As MathJax doesn't work with text mode, to have a consistent method between different outputs, you could use [an R function to write raw HTML or LaTeX code](bookdown.org/yihui/rmarkdown-cookbook/font-color.html#using-an-r-function-to-write-raw-html-or-latex-code) depending on the output. 


```{r, echo = TRUE}
colorize <- function(x, color) {
  if (knitr::is_latex_output()) {
    sprintf("\\textcolor{%s}{%s}", color, x)
  } else if (knitr::is_html_output()) {
    sprintf("<span style='color: %s;'>%s</span>", color, x)
  } else {
    x
  }
}
```

Call: `` r colorize("Hello world!", "blue") `` (enclosed with backsticks)

Rendering: `r colorize("Hello world!", "blue")`

# Writing and including macros files into `.Rmd` 

### File `macros.tex`

```{r, tex, echo = FALSE}
cat(readLines("macros.tex"), sep = "\n")
```

### File `macros.html`

```{r, html, echo = FALSE}
cat(readLines("macros.html"), sep = "\n")
```

### `.Rmd` YAML

```{r, yaml, echo = FALSE}
cat(readLines("examples.Rmd")[1:10], sep = "\n")
```

